---
title: "EDLD 610"
subtitle: "Data visualizations \"in the wild\""  
author: "Cameron S. Kays"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: TRUE
      countIncrementalSlides: TRUE
---

```{r setup, include = FALSE}
# suppress version number in the subdirectory name
options(htmltools.dir.version = FALSE)

#load required packages
library(xaringanthemer)
library(jcolors)
```

```{r xaringan-themer, include = FALSE}
# specify slide font and base color
mono_accent_inverse(
  base_color = "#69c3f4",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Droid Mono"))
```

# The Dataset

The [Core Trends Survey](http://www.pewinternet.org/dataset/jan-3-10-2018-core-trends-survey/) (2018) from the [Pew Research Center](http://www.pewresearch.org).

--

- *N* = 2,002

--

- Collected between January 3rd and January 10th, 2018

--

- Conducted by telephone (75.02% cell phone; 24.98% landline)

---

# Tidying the Dataset

Step 1: Import the data.



--



---

# Tidying the Dataset

.pull-left[

]

--

.pull-right[

]

---

# Tidying the Dataset

Functional but bulky. 


--

Equally functional and far less bulky. 


---

# Tidying the Dataset

.pull-left[

]

.pull-right[

]



---
class: inverse, middle, center

# The END!
